Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-22 paper.qmd
Added details of link plots

### The effect of density

@@

### Hand-written digits
<!--
- NLDR is used to illustrate different ways 1's are drawn
- Use our method to assess is it a reasonable representation
- Demonstrate that it is, except for the anomalies 
-->

@@

>>>>

### The effect of density {#sec-effect-dens}

@@

### Hand-written digits {#sec-mnist}
<!--
- NLDR is used to illustrate different ways 1's are drawn
- Use our method to assess is it a reasonable representation
- Demonstrate that it is, except for the anomalies 
-->

@@

Brushing the high model error in the \gD{} layout, with dense C-shaped data explained in @sec-effect-dens, helps in locating the positions of the related \pD{} points in langevitour view. This process helps in identifying the high model errors that occur due to the sparse end (add the video).

Furthermore, when examining the digit 1 from the MNIST dataset (@sec-mnist), brushing the small cluster in the \gD{} layout helps in locating the positions of the related \pD{} points in langevitour view. This process helps in identifying how close the small cluster to the big cluster (add the video). We can also explore which data corresponds to the twisted pattern of the big cluster (add the video).
